Functional traits complicate the picture of temporal biodiversity change in bird and mammal communities

### 2024-04-24 paper/GEB Submission/manuscript_GEB.tex
rebase?

\begin{table}

\caption{\label{tab:traitTable}Description of the traits included in the analysis broken down by categories at data type.}
\centering
\begin{tabular}[t]{l|l|>{\raggedright\arraybackslash}p{3cm}|>{\raggedright\arraybackslash}p{3cm}}
\hline
Trait & Category & Taxa & Data Type\\
\hline
 & Invertebrate &  & \\
\cline{2-2}
 & Mammals and Birds &  & \\
\cline{2-2}
 & Reptiles &  & \\
\cline{2-2}
 & Fish &  & \\
\cline{2-2}
 & Unknown Vertebrates &  & \\
\cline{2-2}
 & Scavenging &  & \\
\cline{2-2}
 & Fruit &  & \\
\cline{2-2}
 & Nectar &  & \\
\cline{2-2}
 & Seeds &  & \\
\cline{2-2}
\multirow{-10}{*}{\raggedright\arraybackslash Diet} & Other Plant & \multirow{-10}{*}{\raggedright\arraybackslash Bird and Mammal} & \multirow{-10}{*}{\raggedright\arraybackslash percentage consumed}\\
\cline{1-4}
 & Below water surface &  & \\
\cline{2-2}
 & water surface &  & \\
\cline{2-2}
 & ground &  & \\
\cline{2-2}
 & understory &  & \\
\cline{2-2}
 & > 2m, below canopy &  & \\
\cline{2-2}
 & canopy &  & \\
\cline{2-2}
\multirow{-7}{*}{\raggedright\arraybackslash Foraging Strata} & aerial &  & \multirow{-7}{*}{\raggedright\arraybackslash percentage of use}\\
\cline{1-2}
\cline{4-4}
 & yes &  & \\
\cline{2-2}
\multirow{-2}{*}{\raggedright\arraybackslash Pelagic Specialist} & no & \multirow{-9}{*}{\raggedright\arraybackslash Bird} & \\
\cline{1-3}
 & yes &  & \\
\cline{2-2}
\multirow{-2}{*}{\raggedright\arraybackslash Nocturnal} & no & \multirow{-2}{*}{\raggedright\arraybackslash Bird and Mammal} & \\
\cline{1-3}
 & yes &  & \\
\cline{2-2}
\multirow{-2}{*}{\raggedright\arraybackslash Crepuscular} & no &  & \\
\cline{1-2}
 & yes &  & \\
\cline{2-2}
\multirow{-2}{*}{\raggedright\arraybackslash Diurnal} & no & \multirow{-4}{*}{\raggedright\arraybackslash Mammal} & \multirow{-8}{*}{\raggedright\arraybackslash binary}\\
\cline{1-4}
Body Mass & - & Bird and Mammal & continous, in grams\\
\hline
\end{tabular}
\end{table}

@@

@@

\resizebox{\linewidth}{!}{

@@

\multirow{-8}{*}{\raggedright\arraybackslash SES\_FDiv} & \multirow{-6}{*}{\raggedright\arraybackslash random} & \multirow{-3}{2cm}{\raggedright\arraybackslash time series within study} & Corr(Intercept, Year) & -0.01 &  & \\

@@

\multirow{-8}{*}{\raggedright\arraybackslash SES\_FEve} & \multirow{-6}{*}{\raggedright\arraybackslash random} & \multirow{-3}{2cm}{\raggedright\arraybackslash time series within study} & Corr(Intercept, Year) & -0.21 &  & \\

@@

\multirow{-8}{*}{\raggedright\arraybackslash SES\_FRic} & \multirow{-6}{*}{\raggedright\arraybackslash random} & \multirow{-3}{2cm}{\raggedright\arraybackslash time series within study} & Corr(Intercept, Year) & 0.06 &  & \\

@@

\multirow{-8}{*}{\raggedright\arraybackslash log(Jaccard + 1)} & \multirow{-6}{*}{\raggedright\arraybackslash random} & \multirow{-3}{2cm}{\raggedright\arraybackslash time series within study} & Corr(Intercept, Year) & 0.05 &  & \\

@@

\multirow{-8}{*}{\raggedright\arraybackslash log(Species Richness)} & \multirow{-6}{*}{\raggedright\arraybackslash random} & \multirow{-3}{2cm}{\raggedright\arraybackslash time series within study} & Corr(Intercept, Year) & 0.34 &  & \\

@@

\begin{table}

\caption{\label{tab:trendTab}Number of studies that experienced a significant trend in each calculated metric out of 50 total studies.}
\centering
\begin{tabular}[t]{ccccccccc}
\toprule
 & S & Jaccard Similarity & FRic & FEve & FDiv & SES FRic & SES FEve & SES FDiv\\
\midrule
+ & 2 & 0 & 5 & 3 & 1 & 4 & 0 & 1\\
- & 9 & 12 & 2 & 0 & 3 & 1 & 1 & 2\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption{\label{tab:traitTable}Description of the traits included in the analysis broken down by categories at data type.}
\centering
\begin{tabular}[t]{l|l|>{\raggedright\arraybackslash}p{3cm}|>{\raggedright\arraybackslash}p{3cm}}
\hline
Trait & Category & Taxa & Data Type\\
\hline
 & Invertebrate &  & \\
\cline{2-2}
 & Mammals and Birds &  & \\
\cline{2-2}
 & Reptiles &  & \\
\cline{2-2}
 & Fish &  & \\
\cline{2-2}
 & Unknown Vertebrates &  & \\
\cline{2-2}
 & Scavenging &  & \\
\cline{2-2}
 & Fruit &  & \\
\cline{2-2}
 & Nectar &  & \\
\cline{2-2}
 & Seeds &  & \\
\cline{2-2}
\multirow{-10}{*}[4.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash Diet} & Other Plant & \multirow{-10}{*}{\raggedright\arraybackslash Bird and Mammal} & \multirow{-10}{*}{\raggedright\arraybackslash percentage consumed}\\
\cline{1-4}
 & Below water surface &  & \\
\cline{2-2}
 & water surface &  & \\
\cline{2-2}
 & ground &  & \\
\cline{2-2}
 & understory &  & \\
\cline{2-2}
 & > 2m, below canopy &  & \\
\cline{2-2}
 & canopy &  & \\
\cline{2-2}
\multirow{-7}{*}[3\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash Foraging Strata} & aerial &  & \multirow{-7}{*}{\raggedright\arraybackslash percentage of use}\\
\cline{1-2}
\cline{4-4}
 & yes &  & \\
\cline{2-2}
\multirow{-2}{*}[0.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash Pelagic Specialist} & no & \multirow{-9}{*}[0.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash Bird} & \\
\cline{1-3}
 & yes &  & \\
\cline{2-2}
\multirow{-2}{*}[0.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash Nocturnal} & no & \multirow{-2}{*}{\raggedright\arraybackslash Bird and Mammal} & \\
\cline{1-3}
 & yes &  & \\
\cline{2-2}
\multirow{-2}{*}[0.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash Crepuscular} & no &  & \\
\cline{1-2}
 & yes &  & \\
\cline{2-2}
\multirow{-2}{*}[0.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash Diurnal} & no & \multirow{-4}{*}{\raggedright\arraybackslash Mammal} & \multirow{-8}{*}{\raggedright\arraybackslash binary}\\
\cline{1-4}
Body Mass & - & Bird and Mammal & continous, in grams\\
\hline
\end{tabular}
\end{table}

@@

\centering\centering

@@

\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{

@@

\multirow{-8}{*}[1\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash SES\_FDiv} & \multirow{-6}{*}[0.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash random} & \multirow{-3}{2cm}{\raggedright\arraybackslash time series within study} & Corr(Intercept, Year) & -0.01 &  & \\

@@

\multirow{-8}{*}[1\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash SES\_FEve} & \multirow{-6}{*}[0.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash random} & \multirow{-3}{2cm}{\raggedright\arraybackslash time series within study} & Corr(Intercept, Year) & -0.21 &  & \\

@@

\multirow{-8}{*}[1\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash SES\_FRic} & \multirow{-6}{*}[0.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash random} & \multirow{-3}{2cm}{\raggedright\arraybackslash time series within study} & Corr(Intercept, Year) & 0.06 &  & \\

@@

\multirow{-8}{*}[1\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash log(Jaccard + 1)} & \multirow{-6}{*}[0.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash random} & \multirow{-3}{2cm}{\raggedright\arraybackslash time series within study} & Corr(Intercept, Year) & 0.05 &  & \\

@@

\multirow{-8}{*}[1\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash log(Species Richness)} & \multirow{-6}{*}[0.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\raggedright\arraybackslash random} & \multirow{-3}{2cm}{\raggedright\arraybackslash time series within study} & Corr(Intercept, Year) & 0.34 &  & \\

@@

\begin{table}
\centering
\caption{\label{tab:trendTab}Number of studies that experienced a significant trend in each calculated metric out of 50 total studies.}
\centering
\begin{tabular}[t]{ccccccccc}
\toprule
 & S & Jaccard Similarity & FRic & FEve & FDiv & SES FRic & SES FEve & SES FDiv\\
\midrule
+ & 2 & 0 & 5 & 3 & 1 & 4 & 0 & 1\\
- & 9 & 12 & 2 & 0 & 3 & 1 & 1 & 2\\
\bottomrule
\end{tabular}
\end{table}
